### 2013-09-23 image_proc_methods.tex
cherry-picked corrected method ref and merged Kirema MS3 submission

\subsection{Image Zonal Anatomy Segmentation and 3D Model Rendering}
Axial MR T2WI images were manually segmented using the smooth polygon tool in
ITK-SNAP~\cite{Yushkevich2006}, using unique labels for the PZ, CG and AFS. The
gland was segmented from base to apex.  The base was identified below the
bladder, and subsequent images were segmented until the last slice with visible
prostatic tissue was identified caudally. The CG, PZ and AFS were segmented
independently according to their well-established anatomical characteristics on
T2WI.~\cite{Verma2011,Jung2012,Poon1985,Hricak2007,Bonekamp2011} The PZ was
identified by its homogenous high signal intensity on T2WI, which is usually
similar to that of the nearby periprostatic fat. The CG was visualized and
delineated based on its heterogeneous and lower signal intensity as well as its
location (Figure~\ref{fig:mr_anatomy}). Although not readily visible on every
case, the AFS was identified by its low T2 signal intensity and its location
anterior to the central gland.

>>>>

\subsection{Image Zonal Anatomy Segmentation and 3D Model Rendering}
Axial MR T2WI images were manually segmented using the smooth polygon tool in
ITK-SNAP~\cite{Yushkevich2006}, using unique labels for the PZ, CG and AFS. The
gland was segmented from base to apex.  The base was identified below the
bladder, and subsequent images were segmented until the last slice with visible
prostatic tissue was identified caudally. The CG, PZ and AFS were segmented
independently according to their well-established anatomical characteristics on
T2WI.~\cite{Barentsz2012,Jung2012,Poon1985,Hricak2007,Bonekamp2011} The PZ was
identified by its homogenous high signal intensity on T2WI, which is usually
similar to that of the nearby periprostatic fat. The CG was visualized and
delineated based on its heterogeneous and lower signal intensity as well as its
location (Figure~\ref{fig:mr_anatomy}). Although not readily visible on every
case, the AFS was identified by its low T2 signal intensity and its location
anterior to the central gland.
